### 2016-04-23 ch03-lrm/lrm-paper.tex
Some things
Some discussion on LRM results

\begin{table}
\centering
\caption{Local modeling methods used in the Monte Carlo analysis.}
\label{tbl:nparam:methods}
\begin{tabular}{lcccr} \toprule
\textsc{Method} & \DOF & $\nWind$ & $\nth$ & $\Delta$ SNR (dB)\\
\midrule
\color{rgb:red,196;green,160;blue,0} $\ETFE$ & 1 & 0  & 1 & 0 \\
\color{rgb:red,92;green,53;blue,102} $\lrm{7,1,1,1}$ & 15 & 10 & 5 & 4.77121 \\
\color{rgb:red,78;green,154;blue,6} $\lric{7,2,2,2}$ &  15&7 & 8 & 2.73001 \\
\color{rgb:red,32;green,74;blue,135} $\lrm{7,2,2,2}$ &  15&7 & 8 & 2.73001 \\
\color{rgb:red,206;green,92;blue,0} $\lrm{6,2,2,2}$ &  135 & 8 & 2.10853 \\
\color{rgb:red,164;green,0;blue,0} $\lpm{7,4,4}$ &  15&5 & 10 & 1.76091 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Noiseless case}
In the noiseless case, one can observe the approximation error that is made by using the \gls{LRM}, \gls{LPM} and \gls{ETFE}.
For the \gls{ETFE}, it can be seen that the error is very high.
This can be expected since the \gls{ETFE} does not separate transient and leakage contributions.
this error only disappears very slowly by measuring a longer record due to the presence of the leakage term.
As such, \TODO{afschrijven}

>>>>

\begin{table}
\centering
\caption{Local modeling methods used in the Monte Carlo analysis.}
\label{tbl:nparam:methods}
\begin{tabular}{lccccr} 
\toprule
\textsc{Method} & \textsc{Color} & $\nWind$ & $\nth$ & \DOF & $\Delta$ SNR (dB)\\
\midrule
 $\ETFE$ &\color{etfe} --- & 1  & 1  & 0 & 0 \\
 $\lrm{7,1,1,1}$ & \color{lrm7111} --- & 15  & 5 & 10  & 4.77 \\
 $\lric{7,2,2,2}$ &\color{lric7222} --- &   15 & 8 & 7  & 2.73 \\
 $\lrm{7,2,2,2}$ &\color{lrm7222} --- &   15 & 8 & 7  & 2.73 \\
 $\lrm{6,2,2,2}$ &\color{lrm6222} --- &   13 & 8 & 5  & 2.11 \\
 $\lpm{7,4,4}$ &\color{lpm744} --- &   15 & 10 & 5  & 1.76 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Noiseless case}
In the noiseless case, one can observe the approximation error that is made by using the \gls{LRM}, \gls{LPM}, \gls{LRIC} and \gls{ETFE}.
For the \gls{ETFE}, it can be seen that the error is very high.
This can be expected since the \gls{ETFE} does not separate transient/leakage contributions.
Consequently, the leakage contributions (which change over the different Monte Carlo runs), lead to a large variance error for the \gls{ETFE}.
The approximation error of the \gls{LPM} for short datasets ($\nBW \leq 8$) is dominated by the bias error.
The is to be expected since the resonance in the band of interest is modeled using only polynomials instead of the full rational form.
For longer datasets, 
For the \gls{LRM} and \gls{LRIC}, the \gls{RMS} error is already very low for small datasets ($-60 \unit{dB}$ for the first-order method, $-120\unit{dB}$ for second-order methods).
For short datasets ($\nBW \leq 16$), the $\lrm{7,1,1,1}$ error has a bias contribution that is slightly larger ($1$ to $4\unit{dB}$) than the variance contribution.
For larger datasets ($\nBW \geq 16$), this bias contribution starts to diminish significantly as $\bigO{\frac{}{}}$
